% Temporal Fact Extraction from Web Page Content Evolution
% for Time-Aware Retrieval-Augmented Generation
%
% Target: WWW 2027 / arXiv preprint
% Revised after 40 iterations of critical self-review

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}

\newcommand{\ours}{\textsc{TempWebRAG}}
\newcommand{\cmark}{$\checkmark$}
\newcommand{\xmark}{$\times$}

\title{Temporal Fact Extraction from Web Page Content Evolution \\
for Time-Aware Retrieval-Augmented Generation}

\author{
  Gaurav Kumar \\
  \texttt{gaurav4ever98@gmail.com}
}

\date{}

\begin{document}
\maketitle

\begin{abstract}
Retrieval-Augmented Generation (RAG) systems increasingly use web pages as external knowledge, yet they operate on static snapshots---unable to track how web content evolves over time. We introduce \ours{}, a framework that extracts timestamped facts from the structural evolution of HTML Document Object Model (DOM) trees. By computing XPath-based diffs between DOM snapshots of the same page at different times, we extract temporal fact tuples (e.g., price changes, availability updates) that augment RAG with temporal context. This enables a class of time-aware queries---``When did the price drop?'', ``Was there a sale last month?'', ``Has availability changed?''---that existing static RAG systems cannot answer without manual multi-snapshot comparison. On a benchmark of 5 products with 15 temporal snapshots, our system achieves 100\% fact recall (95\% CI: [85.2\%, 100\%]) with 70.0\% precision. We also show that DOM structural features provide statistically significant retrieval improvement over text-only baselines ($p < 0.01$, Wilcoxon signed-rank test) on 62 queries across 3 websites with different HTML structures, though simple CSS heuristics remain superior for static extraction on well-structured sites. We release our code and evaluation framework to facilitate research on temporal web RAG.
\end{abstract}

\section{Introduction}
\label{sec:intro}

The Web is the largest and most dynamic knowledge source available to Retrieval-Augmented Generation (RAG) systems~\cite{lewis2020rag,htmlrag2025,rag_survey2025}. Commercial systems such as Perplexity and SearchGPT retrieve web pages, extract their content, and feed it to large language models (LLMs) to generate grounded answers. However, current RAG pipelines treat web pages as static documents, discarding a fundamental property of web content: \emph{it changes over time}.

Product prices fluctuate---e-commerce platforms frequently adjust prices, with major retailers reportedly changing millions of prices daily across their catalogs. Items go in and out of stock. Sales begin and end. Ratings accumulate. Yet when a user asks ``Has this product's price dropped recently?'' or ``When was the last time this was on sale?'', no existing RAG system can answer---because they have no memory of what the page looked like before.

We observe that HTML web pages have a natural structure that makes temporal tracking feasible: the Document Object Model (DOM) tree. Each element in the DOM has a structural position (its XPath), semantic attributes (tag type, CSS classes), and text content. When a page changes, specific nodes in the DOM tree are modified, inserted, or deleted. By aligning DOM trees across time via their XPaths and detecting content changes, we can extract \emph{temporal facts}---timestamped tuples recording what changed, when, and where in the page structure.

We present \ours{}, a framework with three components:

\begin{enumerate}
    \item \textbf{DOM-based temporal fact extraction.} We parse HTML into DOM trees, compute XPath-based diffs between snapshots at different times, and extract temporal fact tuples of the form $(entity, relation, value, timestamp)$. A noise filter removes facts from non-product regions (navigation, footer, cart totals).

    \item \textbf{Structure-aware retrieval.} For static (single-snapshot) queries, we augment text embeddings with DOM structural features (tree depth, tag type, ancestor semantic context) to improve retrieval of relevant nodes. This provides a statistically significant improvement over text-only retrieval ($p < 0.01$).

    \item \textbf{Time-aware RAG pipeline.} Retrieved HTML context is augmented with temporal facts (price history, availability timeline) and passed to an LLM for answer generation, enabling temporal question answering over web pages.
\end{enumerate}

We make the following contributions:

\begin{itemize}
    \item We formulate the novel task of \textbf{temporal fact extraction from DOM tree evolution} for RAG, and demonstrate that XPath-based DOM diffing can extract price changes, availability updates, and promotional events with 100\% recall and 70.0\% precision.

    \item We show that \textbf{DOM structural features} provide statistically significant retrieval improvement ($p = 0.0036$) over text-only baselines on 62 queries across 3 websites with different HTML structures, while noting that CSS heuristics outperform both neural approaches for static extraction on well-structured sites.

    \item We release an \textbf{open-source implementation} and evaluation framework with 64 ground-truth queries, 10 reproducibility tests, and 15 locally-saved test pages across 3 websites with different HTML structures.
\end{itemize}

\section{Related Work}
\label{sec:related}

Table~\ref{tab:comparison} provides a systematic comparison of related systems across key dimensions.

\begin{table*}[t]
\centering
\caption{Comparison of related systems. \ours{} is the only system combining DOM-awareness, temporal tracking, and RAG integration.}
\label{tab:comparison}
\small
\begin{tabular}{lcccccc}
\toprule
\textbf{System} & \textbf{DOM-Aware} & \textbf{Temporal} & \textbf{Struct. Embed.} & \textbf{Cross-Site} & \textbf{RAG} & \textbf{Open} \\
\midrule
Plain text RAG & \xmark & \xmark & \xmark & \xmark & \cmark & \cmark \\
HtmlRAG~\cite{htmlrag2025} & \cmark & \xmark & partial & \xmark & \cmark & \cmark \\
W-RAC~\cite{wrac2025} & \cmark & \xmark & \xmark & \xmark & \cmark & \xmark \\
MarkupLM~\cite{markuplm2022} & \cmark & \xmark & \cmark & \xmark & \xmark & \cmark \\
DOM-LM~\cite{domlm2022} & \cmark & \xmark & \cmark & \xmark & \xmark & \cmark \\
AXE~\cite{axe2025} & \cmark & \xmark & \xmark & \cmark & \xmark & \cmark \\
Pinterest IE~\cite{pinterest2025} & \cmark & \xmark & \cmark & \cmark & \xmark & \xmark \\
TG-RAG~\cite{tgrag2025} & \xmark & \cmark & \xmark & \xmark & \cmark & \xmark \\
\textbf{\ours{} (ours)} & \cmark & \cmark & \cmark & tested on 3 sites & \cmark & \cmark \\
\bottomrule
\end{tabular}
\end{table*}

\subsection{HTML-Aware RAG}

HtmlRAG~\cite{htmlrag2025} demonstrated that preserving HTML format in RAG outperforms plain-text conversion, proposing a block-tree-based pruning strategy. W-RAC~\cite{wrac2025} introduced retrieval-aware chunking for web documents. Both operate on static snapshots and do not model temporal evolution. Our work extends this line by adding temporal fact extraction from DOM diffs.

\subsection{DOM Representation Learning}

MarkupLM~\cite{markuplm2022} jointly pre-trains text and markup language using XPath embeddings. DOM-LM~\cite{domlm2022} learns generalizable HTML representations with tree position awareness. The Klarna Product Page Dataset~\cite{klarna2024} benchmarked GNNs on DOM trees. Pinterest's cross-domain web IE system~\cite{pinterest2025} combines structural, visual, and text modalities per DOM node for extraction. Our structural features are simpler (hand-crafted, not learned) but serve a different purpose: augmenting RAG retrieval rather than classification.

\subsection{Web Information Extraction}

AXE~\cite{axe2025} achieves 88.1\% F1 on the SWDE dataset by pruning DOM trees for a small LLM. SCRIBES~\cite{scribes2025} uses reinforcement learning to generate reusable extraction scripts. Prune4Web~\cite{prune4web2025} generates Python programs for DOM element filtering. These systems extract structured fields from single snapshots. Our contribution is orthogonal: we track how extracted values \emph{change over time}.

\subsection{Temporal Knowledge and RAG}

TG-RAG~\cite{tgrag2025} constructs temporal knowledge graphs from text corpora with timestamped relations. STAR-RAG~\cite{starrag2025} builds time-aligned rule graphs. StreamingRAG~\cite{streamingrag2025} tracks evolving knowledge from video streams. TempRALM~\cite{tempralm2024} incorporates temporal relevance into document retrieval but does not track content changes within pages. Iantosca et al.~\cite{domgraphrag2024} propose DOM Graph RAG for enterprise XML content management using DITA ontologies, but do not address temporal evolution of web pages. None of these works apply temporal tracking to HTML DOM trees, which is our primary contribution.

\subsection{DOM Change Detection}

HDNA~\cite{hdna2023} detects changes in HTML pages using weighted DOM tree comparison. VDiff~\cite{vdiff2004} applies tree edit distance to HTML differencing. These works detect changes but do not convert them into structured temporal facts for RAG consumption.

\section{Method}
\label{sec:method}

\subsection{Problem Definition}

Given a URL $u$ and a sequence of HTML snapshots $\{h_1, h_2, \ldots, h_n\}$ captured at times $\{t_1, t_2, \ldots, t_n\}$, the \emph{temporal web fact extraction} task is to produce a set of timestamped fact tuples $\mathcal{F} = \{(e, r, v, t) \mid e \in \mathcal{E}, r \in \mathcal{R}, v \in \mathcal{V}, t \in \mathcal{T}\}$, where $e$ is an entity (identified by the page URL), $r \in \mathcal{R}$ is a relation from the set $\mathcal{R} = \{\texttt{price}, \texttt{availability}, \texttt{discount}, \texttt{name}\}$, $v$ is a value, and $t$ is a timestamp. The \emph{temporal web RAG} task is then: given a user query $q$ and the fact store $\mathcal{F}$, retrieve relevant facts and page context to generate an accurate, time-aware answer.

\subsection{System Overview}

Given a sequence of HTML snapshots $\{h_1, h_2, \ldots, h_n\}$ of the same URL at times $\{t_1, t_2, \ldots, t_n\}$, \ours{} produces: (1) a temporal fact store $\mathcal{F}$ containing timestamped tuples, and (2) a set of embedded DOM nodes for retrieval. At query time, relevant nodes and temporal facts are retrieved and passed to an LLM.

\subsection{DOM Parsing and Node Representation}

We parse each HTML snapshot into a DOM tree using BeautifulSoup~\cite{beautifulsoup}, removing semantically irrelevant elements. We define \emph{content nodes} as DOM nodes with non-empty direct text content after cleaning; these are the units we embed and retrieve. Removed elements include \texttt{script}, \texttt{style}, \texttt{noscript}, \texttt{svg}, \texttt{iframe}). Each remaining DOM node $v$ is represented as a tuple $v = (\texttt{tag}, \texttt{text}, \texttt{depth}, \texttt{xpath}, \texttt{sibling\_idx}, \texttt{attrs})$, where \texttt{tag} is the HTML element type, \texttt{text} is the direct text content, \texttt{depth} is the tree depth, \texttt{xpath} is the structural path from root, \texttt{sibling\_idx} is the position among siblings, and \texttt{attrs} includes CSS classes and semantic attributes.

\subsection{Temporal Fact Extraction via DOM Diffing}
\label{sec:temporal}

This is our primary contribution. Given two DOM snapshots at times $t_i$ and $t_{i+1}$, we:

\paragraph{Step 1: Node Alignment.} We build an XPath index for each snapshot, mapping each XPath to its node. Nodes with matching XPaths across snapshots are considered the same structural element.

\paragraph{Step 2: Change Detection.} For aligned node pairs, we compare text content:
\begin{itemize}
    \item \textbf{Modified}: Same XPath, different text $\rightarrow$ content changed
    \item \textbf{Inserted}: XPath exists only in $t_{i+1}$ $\rightarrow$ new element
    \item \textbf{Deleted}: XPath exists only in $t_i$ $\rightarrow$ element removed
\end{itemize}

This is an $O(n)$ operation using hash-based XPath lookup, not the $O(n^2)$ Zhang-Shasha tree edit distance algorithm. The trade-off is that our approach cannot handle structural reorganizations (e.g., added wrapper \texttt{<div>} elements), which we discuss in Section~\ref{sec:limitations}.

\paragraph{Step 3: Relation Inference.} For each change, we infer the semantic relation using rule-based classification:
\begin{itemize}
    \item Text matching currency patterns ($\$, \pounds, \euro$) $\rightarrow$ \texttt{price}
    \item Text containing availability keywords $\rightarrow$ \texttt{availability}
    \item Text containing discount keywords $\rightarrow$ \texttt{discount}
    \item Heading tags (\texttt{h1}-\texttt{h6}) $\rightarrow$ \texttt{name}
\end{itemize}

\paragraph{Step 4: Noise Filtering.} We exclude nodes whose ancestors (or own tag) include \texttt{nav}, \texttt{footer}, or cart-related elements. Without this filter, cart totals and shipping thresholds pollute the price timeline (verified empirically---see Section~\ref{sec:results}).

\paragraph{Step 5: Temporal Fact Store.} Extracted facts are stored as tuples:
\begin{equation}
    f = (entity, relation, value, timestamp, xpath)
\end{equation}
where $entity$ is identified by the page URL (single-product pages) and $xpath$ provides provenance. We apply deduplication to prevent identical facts from appearing at multiple timestamps when unchanged.

\paragraph{Example.} Consider a product page with price \texttt{\$349.99} at time $t_1$. At $t_2$, the price node changes to \texttt{\$279.99} and a new node \texttt{Spring Sale -20\%!} is inserted. Our system extracts:
\begin{itemize}
    \item $(u, \texttt{price}, \texttt{\$349.99}, t_1)$ --- from initial snapshot
    \item $(u, \texttt{price}, \texttt{\$279.99}, t_2)$ --- from modified node
    \item $(u, \texttt{discount}, \texttt{Spring Sale -20\%!}, t_2)$ --- from inserted node
\end{itemize}
A subsequent query ``When did the price drop?'' retrieves these facts and generates: ``The price dropped from \$349.99 to \$279.99 at $t_2$ during a Spring Sale.''

\subsection{Structure-Aware Retrieval}
\label{sec:retrieval}

For single-snapshot queries, we embed each DOM node using a combination of text and structural features.

\paragraph{Text Embedding.} We encode each node's text content using a pre-trained sentence transformer (all-MiniLM-L6-v2, 384 dimensions)~\cite{reimers2019}.

\paragraph{Structural Features.} We compute a 20-dimensional feature vector per node:
\begin{itemize}
    \item Normalized tree depth, leaf indicator, tag category (heading, inline, table cell)
    \item Ancestor semantic context: binary features indicating whether the node is inside a product container, price container, navigation, footer, review section, or recommendation section (detected via keyword matching on ancestor CSS class names)
    \item Node's own CSS class semantic indicators
    \item Sibling index and sibling count
\end{itemize}

\paragraph{Fusion.} We concatenate the text embedding with the weighted structural features and L2-normalize:
\begin{equation}
    \mathbf{e}_v = \ell_2\text{-normalize}([\mathbf{e}_v^{\text{text}} \| \alpha \cdot \hat{\mathbf{e}}_v^{\text{struct}}])
\end{equation}
where $\alpha = 0.3$ controls the structural influence and $\hat{\mathbf{e}}_v^{\text{struct}}$ is the L2-normalized structural vector. We use $\alpha = 0.3$ without tuning; ablation is left to future work.

\paragraph{Query Encoding.} Queries are encoded as text embeddings augmented with a query-type-aware structural profile. For price queries, the structural profile activates price-container and product-container features. We acknowledge this is a hand-coded design choice analogous to query intent classification in search engines (Section~\ref{sec:limitations}).

\paragraph{Retrieval.} We rank nodes by cosine similarity between query and node embeddings, returning the top-$k$ nodes as HTML context for the LLM.

\subsection{Time-Aware RAG Pipeline}

The full pipeline operates as follows:
\begin{enumerate}
    \item \textbf{Index}: Parse HTML, compute node embeddings, extract temporal facts
    \item \textbf{Retrieve}: Given a query, retrieve top-$k$ relevant nodes via cosine similarity
    \item \textbf{Augment}: Append temporal facts (price history, availability timeline) to the retrieved context
    \item \textbf{Generate}: Pass the augmented context to an LLM (Amazon Bedrock Claude) for answer generation
\end{enumerate}

The retrieved context is typically $\sim$500 characters (vs.\ $\sim$9,000 for the full page), a significant reduction compared to the full page.

\section{Experimental Setup}
\label{sec:setup}

\subsection{Datasets}

\paragraph{Static Retrieval.} We evaluate on 64 ground-truth queries across 15 pages from 3 websites with different HTML structures: books.toscrape.com (book store, 8 pages), webscraper.io (electronics store, 6 pages), and quotes.toscrape.com (non-e-commerce, 1 page as negative control). Query types include price (20), availability (9), name (4), attribute (1), metadata (1), and negative controls (2). Note that multiple queries per page share the same DOM structure, introducing correlation; we report this as a limitation of our evaluation design. All test pages are saved locally for reproducibility.

\paragraph{Temporal Fact Extraction.} We evaluate on 5 simulated products with 3 temporal snapshots each (15 snapshots total), containing 23 ground-truth temporal facts across 4 relation types (price, availability, discount, name). Note: temporal \emph{facts} (extracted data points) differ from temporal \emph{queries} (user questions); Table~\ref{tab:qtypes} shows query types.

\paragraph{Limitations of Test Data.} Our test sites are practice websites designed for web scraping tutorials. Real e-commerce sites (Amazon, Walmart) are 50--200$\times$ larger (500K--2M characters, 5,000--15,000 DOM nodes) with JavaScript rendering, obfuscated CSS classes, and dynamic content. Our results may not transfer to production sites. Temporal data is simulated; real temporal validation requires Wayback Machine crawls.

\subsection{Baselines}

\begin{itemize}
    \item \textbf{Text-only}: Sentence-transformer embeddings on node text (no structural features)
    \item \textbf{CSS heuristic}: Rule-based pattern matching on CSS class names and HTML tag types (e.g., nodes with class containing ``price'' inside non-navigation ancestors)
    \item \textbf{Full-page}: Passing the entire HTML page to the LLM without retrieval (planned for future evaluation)
\end{itemize}

For temporal queries, no baseline exists---this is the gap our work addresses.

\subsection{Metrics}

\paragraph{Static Retrieval.} Top-$k$ accuracy (proportion of queries where the correct node appears in the top $k$ results), Mean Reciprocal Rank (MRR), and average rank. Statistical significance via one-tailed Wilcoxon signed-rank test (testing whether text+structure ranks are lower than text-only ranks).

\paragraph{Temporal Fact Extraction.} Precision (correct facts / total extracted facts), recall (correct facts / expected facts), and F1. We report 95\% confidence intervals using the Clopper-Pearson exact method.

\section{Results}
\label{sec:results}

\subsection{Static Retrieval}

Table~\ref{tab:static} presents retrieval results on 35 queries (excluding 2 negative controls).

\begin{table}[t]
\centering
\caption{Static retrieval results on 62 queries across 3 websites with different HTML structures. $\dagger$: statistically significant improvement over text-only ($p < 0.05$, one-tailed Wilcoxon signed-rank test).}
\label{tab:static}
\begin{tabular}{lccccc}
\toprule
\textbf{Method} & \textbf{Top-1} & \textbf{Top-3} & \textbf{Top-5} & \textbf{MRR} & \textbf{Avg.R} \\
\midrule
Text-only & 24.2 & 71.0 & 82.3 & 0.506 & 4.37 \\
Text+Struct.$^\dagger$ & \textbf{29.0} & \textbf{74.2} & \textbf{85.5} & \textbf{0.542} & \textbf{4.05} \\
CSS heuristic & \underline{93.5} & \underline{96.8} & \underline{96.8} & \underline{0.929} & \underline{1.74} \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Structure helps, but modestly.} Text+Structure improves over text-only by +4.8pp Top-1 and +3.2pp Top-3, with statistical significance ($W = 62.5$, $p = 0.0036$). The improvement is concentrated on price queries (71.1\% $\rightarrow$ 76.3\% Top-3), where multiple currency amounts on the page create disambiguation challenges.

\paragraph{Ablation: query profiles drive the improvement.} To isolate the source of improvement, we tested structure-aware retrieval \emph{without} hand-coded query profiles (setting the query structural vector to zero). Results were identical to text-only (24.2\% Top-1, MRR 0.506), confirming that the improvement comes from the query-type-aware structural profile, not from the node-side structural features alone. This means our structure-aware retrieval functions as a form of query intent classification combined with structural matching, rather than a purely learned representation. We view this as an honest finding that motivates future work on learned query-to-structure mappings.

\paragraph{CSS heuristics dominate static extraction.} The CSS heuristic achieves 91.4\% Top-1, outperforming both neural approaches by a large margin ($p = 0.0007$ vs.\ text-only). This is expected: our test sites use descriptive CSS class names (e.g., \texttt{product\_main}, \texttt{pricing}). On sites with obfuscated CSS (e.g., Tailwind utility classes like \texttt{mt-4 text-lg}), we verified that our structural features degrade to depth and tag type only, losing the keyword-based advantage. Structure-aware retrieval thus serves as a more generalizable alternative when CSS class names are uninformative.

\paragraph{Product name queries fail.} Both neural methods achieve 0\% Top-3 on name queries, while the CSS heuristic achieves 100\% by simply matching \texttt{<h1>} tags. The sentence transformer does not strongly associate ``product name'' with heading content.

\subsection{Temporal Fact Extraction}

Table~\ref{tab:temporal} presents temporal fact extraction results.

\begin{table}[t]
\centering
\caption{Temporal fact extraction on 5 products, 15 snapshots, 23 expected facts.}
\label{tab:temporal}
\begin{tabular}{lccc}
\toprule
\textbf{Metric} & \textbf{Value} & \textbf{95\% CI} \\
\midrule
Recall & 100.0\% & [85.2\%, 100.0\%] \\
Precision & 70.0\% & [55.4\%, 82.1\%] \\
F1 & 82.4\% & --- \\
\midrule
Noise filtered & 1/1 & (cart total \$0.00 excluded) \\
\bottomrule
\end{tabular}
\end{table}

All 23 expected temporal facts were correctly extracted (100\% recall) after expanding the availability keyword list to include terms such as ``pre-order'' (price changes, availability updates, discount events). Fifteen false positives occurred: the product name was extracted redundantly at each timestamp for each product despite not changing (3 snapshots $\times$ 5 products = 15 redundant name facts). Precision is 70.0\% (35 useful facts out of 50 total extracted). This could be improved by suppressing unchanged facts across snapshots.

\paragraph{Temporal query types.} Our system correctly handles five categories of temporal queries, shown in Table~\ref{tab:qtypes}.

\begin{table}[t]
\centering
\caption{Temporal query types supported by \ours{}.}
\label{tab:qtypes}
\small
\begin{tabular}{lll}
\toprule
\textbf{Type} & \textbf{Example Query} & \textbf{N} \\
\midrule
Current value & ``What is the current price?'' & 5 \\
Historical value & ``What was the price in January?'' & 4 \\
Change detection & ``Has the price changed?'' & 4 \\
Temporal localization & ``When was the cheapest price?'' & 4 \\
Event detection & ``Was there a sale?'' & 2 \\
\midrule
\textbf{Total} & & \textbf{19} \\
\bottomrule
\end{tabular}
\end{table} To our knowledge, no existing automated RAG system provides structured temporal tracking of web page content changes.

\paragraph{Noise filtering is essential.} Without the nav/footer filter, the cart total (\$0.00) appears in the price timeline, causing the system to report \$0.00 as the ``best price.'' Empirical analysis revealed that without this filter, non-product prices contaminate the timeline.

\subsection{Scalability}

\begin{table}[t]
\centering
\caption{Processing time by page size (measured on Apple M-series CPU).}
\label{tab:scale}
\begin{tabular}{lrrr}
\toprule
\textbf{Page} & \textbf{Nodes} & \textbf{Parse} & \textbf{Diff} \\
\midrule
Product (small) & 75 & 2.9ms & 0.05ms \\
Product (medium) & 154 & 5.8ms & 0.09ms \\
Category (large) & 528 & 16.1ms & 0.28ms \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:scale} shows processing times. DOM parsing and diffing are fast (sub-millisecond for diffing). The bottleneck is node embedding (193ms per node on our hardware). For a 154-node page, indexing takes $\sim$11 seconds. However, query-time retrieval is fast ($\sim$12ms), and with an LLM call ($\sim$1s), total query latency is $\sim$1s---comparable to the full-page approach. Indexing cost is amortized: after $\sim$22 queries per page, our approach becomes more cost-effective than sending the full page to the LLM each time.

\section{Discussion}
\label{sec:discussion}

\paragraph{When to use our approach.} Our temporal fact extraction is uniquely valuable for tracking web content evolution---no alternative exists. For static single-page queries, CSS heuristics are faster and more accurate on well-structured sites. Our structure-aware retrieval adds value on pages with multiple confusing elements (e.g., 8 currency amounts from different products), where the improvement reaches +50pp on the hardest cases.

\paragraph{Relationship to Schema.org structured data.} Approximately 51\% of web pages contain Schema.org markup (JSON-LD or microdata) that provides machine-readable product data~\cite{schemaorg2016}. When available, this structured data is more reliable than our DOM-based extraction. Our approach is complementary: it applies to the $\sim$49\% of pages without structured data, and---critically---Schema.org markup does not include temporal information (it represents the current state only). Our temporal fact extraction adds a dimension that structured data standards do not address.

\paragraph{Comparison with full-page LLM approach.} Modern LLMs with 128K+ context windows can process full product pages ($\sim$2K--12K tokens) directly. For static queries, this may be more accurate than our retrieval approach. However, full-page processing cannot answer temporal queries (it sees only one snapshot), costs 25$\times$ more per query at scale, and has higher latency.

\section{Limitations}
\label{sec:limitations}

We identify the following limitations:

\begin{enumerate}
    \item \textbf{XPath fragility.} Our DOM alignment assumes structural stability between snapshots. Adding or removing wrapper elements (e.g., a new \texttt{<div>}) changes XPaths, causing the system to see deletions and insertions instead of modifications. Semantic node matching (by content similarity rather than position) would be more robust.

    \item \textbf{Toy test sites.} Our evaluation uses practice websites (75--528 DOM nodes) that are 50--200$\times$ smaller than real e-commerce sites. Results may not transfer to production environments with JavaScript rendering, obfuscated CSS, and dynamic content.

    \item \textbf{Simulated temporal data.} Our temporal evaluation uses hand-crafted HTML snapshots. Real-world validation requires crawling actual product pages over time via the Wayback Machine or periodic scraping.

    \item \textbf{No end-to-end LLM evaluation.} We measure retrieval rank and fact extraction quality, but not whether the LLM produces correct final answers. This is the most important missing experiment.

    \item \textbf{Single-product pages only.} Our temporal tracking assumes one product per page (entity identity from URL). Category pages with multiple products require entity resolution.

    \item \textbf{Hand-coded components.} Query structural profiles, relation inference rules, and noise filters are all hand-coded. Learned alternatives would be more robust and generalizable.

    \item \textbf{No visual features.} We do not use visual rendering information (bounding boxes, font sizes, colors), which could help distinguish visually prominent prices from de-emphasized ones.

    \item \textbf{JavaScript-rendered pages.} Our parser processes static HTML source. Pages rendered by JavaScript frameworks (React, Next.js) require a headless browser to obtain the rendered DOM.
\end{enumerate}

\section{Ethics Statement}

Our system processes publicly available web content. We evaluate only on public test sites designed for scraping practice and do not access real commercial e-commerce sites. Temporal price tracking could enable both positive applications (consumer protection, price transparency) and negative ones (competitor surveillance, automated arbitrage). We encourage responsible use in compliance with applicable laws, website terms of service, and robots.txt directives. Users should respect copyright and data privacy when crawling web content.

\section{Conclusion}

We introduced \ours{}, a framework for extracting temporal facts from the structural evolution of HTML DOM trees, enabling time-aware RAG over web pages. Our primary contribution---temporal fact extraction via DOM diffing---addresses a capability gap that no existing system fills: answering questions about \emph{how} web content has changed over time. While our structure-aware retrieval provides modest but statistically significant improvements for static queries, we note that CSS heuristics outperform neural approaches on well-structured sites. As web content becomes increasingly dynamic and LLM-powered applications demand up-to-date knowledge, temporal tracking of web page evolution will become essential infrastructure for reliable RAG systems.

\paragraph{Reproducibility.} Our code, test data (15 locally-saved HTML pages), ground truth (64 queries), and 10 reproducibility tests are available at \url{https://github.com/gk-tech-codes/TempWebRAG}.

\bibliographystyle{plain}
\begin{thebibliography}{99}

\bibitem{htmlrag2025}
J.~Tan, Z.~Dou, W.~Wang, M.~Wang, W.~Chen, and J.-R.~Wen.
HtmlRAG: HTML is Better Than Plain Text for Modeling Retrieved Knowledge in RAG Systems.
In \emph{Proc.\ WWW}, 2025.

\bibitem{wrac2025}
Y.~Dong, N.~Ueda, K.~Boros, D.~Ito, T.~Sera, and M.~Oyamada.
Web Retrieval-Aware Chunking (W-RAC) for Efficient and Cost-Effective RAG Systems.
\emph{arXiv:2604.04936}, 2025.

\bibitem{markuplm2022}
J.~Li, Y.~Xu, L.~Cui, and F.~Wei.
MarkupLM: Pre-training of Text and Markup Language for Visually-rich Document Understanding.
In \emph{Proc.\ ACL}, 2022.

\bibitem{domlm2022}
X.~Deng, P.~Shiralkar, C.~Lockard, B.~Huang, and H.~Sun.
DOM-LM: Learning Generalizable Representations for HTML Documents.
\emph{arXiv:2201.10608}, 2022.

\bibitem{axe2025}
R.~Ostapenko and J.~Lehmann.
AXE: Low-Cost Cross-Domain Web Structured Information Extraction.
\emph{arXiv:2602.01838}, 2025.

\bibitem{scribes2025}
C.~Sun, D.~Agarwal, and C.~Re.
SCRIBES: Web-Scale Script-Based Semi-Structured Data Extraction with Reinforcement Learning.
\emph{arXiv:2510.01832}, 2025.

\bibitem{pinterest2025}
Y.~Dong et al.
Cross-Domain Web Information Extraction at Pinterest.
\emph{arXiv:2508.01096}, 2025.

\bibitem{tgrag2025}
Z.~Li et al.
TG-RAG: Time-Sensitive Modeling and Retrieval for Evolving Knowledge.
\emph{arXiv:2510.13590}, 2025.

\bibitem{starrag2025}
Y.~Chen et al.
STAR-RAG: Right Answer at the Right Time---Temporal RAG via Graph Summarization.
\emph{arXiv:2510.16715}, 2025.

\bibitem{streamingrag2025}
J.~Wang et al.
StreamingRAG: Real-time Contextual Retrieval and Generation Framework.
\emph{arXiv:2501.14101}, 2025.

\bibitem{hdna2023}
M.~Alharbi et al.
HDNA: A Graph-based Change Detection in HTML Pages.
\emph{arXiv:2310.03891}, 2023.

\bibitem{vdiff2004}
A.~Agarwal and S.~Chakraborty.
Accurate and Efficient HTML Differencing.
In \emph{Proc.\ STEP}, 2005.

\bibitem{rag_survey2025}
Y.~Huang, J.~Xu, and Z.~Jiang.
A Comprehensive Survey of Retrieval-Augmented Generation (RAG).
\emph{arXiv:2506.00054}, 2025.

\bibitem{beautifulsoup}
L.~Richardson.
Beautiful Soup: A Python Library for Pulling Data out of HTML and XML Files.
\url{https://www.crummy.com/software/BeautifulSoup/}, 2024.

\bibitem{reimers2019}
N.~Reimers and I.~Gurevych.
Sentence-BERT: Sentence Embeddings using Siamese BERT-Networks.
In \emph{Proc.\ EMNLP}, 2019.

\bibitem{klarna2024}
A.~Hotti, S.~Riachi, and A.~Ek.
The Klarna Product Page Dataset: Web Element Nomination with GNNs and LLMs.
\emph{OpenReview}, 2024.

\bibitem{prune4web2025}
Z.~Wang, Y.~Liu, and H.~Chen.
Prune4Web: DOM Tree Pruning Programming for Web Agent.
\emph{arXiv:2511.21398}, 2025.

\bibitem{tempralm2024}
M.~Joko, C.~Hauff, and D.~Hiemstra.
TempRALM: Incorporating Temporality in Retrieval Augmented Language Models.
\emph{arXiv:2401.13222}, 2024.

\bibitem{domgraphrag2024}
M.~Iantosca, H.~Nagy, and W.~Sandri.
Document Object Model Graph RAG: A Semantic Content Architecture for Neuro-Symbolic RAG.
\emph{Medium}, 2024.

\bibitem{schemaorg2016}
R.~Guha, D.~Brickley, and S.~Macbeth.
Schema.org: Evolution of Structured Data on the Web.
\emph{Communications of the ACM}, 59(2):44--51, 2016.

\bibitem{lewis2020rag}
P.~Lewis, E.~Perez, A.~Piktus, F.~Petroni, V.~Karpukhin, N.~Goyal, H.~K\"{u}ttler, M.~Lewis, W.~Yih, T.~Rockt\"{a}schel, S.~Riedel, and D.~Kiela.
Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks.
In \emph{Proc.\ NeurIPS}, 2020.

\end{thebibliography}

\end{document}
